The SMT Competition 2015--2018

### 2019-04-15 2018/report/SMT-COMP.tex
conclusion

Further development of the competition should be undertaken with care,
keeping in mind that major changes require not just the competition
organizers, but also participants to adapt.  Immediate action items
for next year's organizers are
\begin{itemize}
\item the inclusion of {\tt check-sat} commands with unknown status in
  the \apptrack, and
\item the definition of competition-wide rankings for the \apptrack 
  and \ucoretrack.
\end{itemize}

>>>>

\paragraph{The Next Competition}

Preparations for the 2019 iteration of the competition are underway and a number of changes have already been decided. These include

\begin{itemize}
	\item the inclusion of {\tt check-sat} commands with unknown status in
  the \apptrack, 
  	\item the removal of non-competitive divisions and the filtering of benchmarks to exclude those seen as \emph{trivial} (taken as those solved by all competitors in the previous competition in less than 1 second)  
  	\item the introduction of a new experimental \emph{model validation track} with a single QF\_BV division where the models produced by solvers are checked,
	\item the introduction of a new \emph{industrial challenge track} consisting of unsolved benchmarks submitted specifically for the track, and
	\item the removal of the notion of competition-wide scoring.
\end{itemize}

\paragraph{The Future}

Looking to the future of the competition, it is clear that further development should be undertaken with care,
keeping in mind that major changes require not just the competition
organizers, but also participants to adapt.
